% -*- coding: utf-8 -*-


\begin{zhaiyao}
2015年深度学习和强化学习的首次结合在雅达利49类游戏上取得巨大成功，但是强化学习算法应用的过程中仍存在大量的问题，如算法稳定性差，可扩展性差等，这些问题阻碍了其进一步的应用。举例来说，学者常常会在雅达利平台上测试算法的性能，而传统的强化学习算法只能解决一些简单的游戏，并且在不同的游戏中其表现差距很大。为了进一步提升强化学习算法的学习效率和泛化性能，文章提出了名为AlphaAtari的强化学习算法，在保证算法高效性的同时，极大的提升算法的稳定性和可扩展性。
为了达到这种效果，文章首先提出一套完整的无模型强化学习统一框架，然后通过引入策略族来丰富文章的采样策略。此外，文章针对性的设计了面向耦合多参数的自适应控制器来自动地调整算法中的各种具有强关联性的超参数。实验表明文章的算法在雅达利全部57个游戏中在人类归一化平均得分这一指标上超越了当前的得分最高的算法Agent57，意味着这项工作使文章向实现通用人工智能迈出了坚实的一步。
\end{zhaiyao}




\begin{guanjianci}
强化学习；深度学习；瓦砾编码；数据分析
\end{guanjianci}



\begin{abstract}
In 2015, the first combination of deep learning and reinforcement learning achieved great success in Atari 49 games, but there are still a lot of problems in the application of reinforcement learning algorithms, such as poor algorithm stability and poor scalability. These problems hinder its further application. For example, researchers often test the performance of algorithms on the Atari platform, while traditional reinforcement learning algorithms can only solve some simple games, and their performance varies greatly in different games. In order to further improve the learning efficiency and generalization performance of the reinforcement learning algorithm, this paper proposes a reinforcement learning algorithm called AlphaAtari, which greatly improves the stability and scalability of the algorithm while ensuring the efficiency of the algorithm.
In order to achieve this effect, this paper first proposes a complete unified framework for model-free reinforcement learning, and then enriches the sampling strategy of this article by introducing a strategy family. In addition, this paper specifically designs an adaptive controller for coupled multi-parameters to automatically adjust various hyperparameters with strong correlation in the algorithm. Experiments show that our algorithm has achieved the highest average human normalized  scores in all 57 games of Atari, surpassing the current highest-scoring algorithm Agent57, and has taken a solid step towards the realization of general artificial intelligence.
\end{abstract}



\begin{keywords}
reinforcement learning; deep learning; tile coding; data mining
\end{keywords} 